---
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    css: styles_flex.css
params: 
    set_title: ""
title: "`r params$set_title`"
---



```{r setup, include=FALSE}
library(flexdashboard)
library(rAmCharts)
library(antaresFlowbased)
library(manipulateWidget)
library(flowBasedClustering)
```


Hour 1 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 1
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 2 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 2
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 3 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 3
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 4 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 4
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 5 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 5
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 6 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 6
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 7 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 7
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 8 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 8
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 9 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 9
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```


Hour 10 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 10
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 11 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 11
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 12 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 12
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```




Hour 13 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 13
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 14 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 14
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 15 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 15
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 16 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 16
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 17 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 17
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 18 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 18
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 19 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 19
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 20 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 20
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 21 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 21
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 22 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 22
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```



Hour 23 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 23
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```


Hour 24 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 24
```

Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
clusterPlot(data, "BE", "FR", hour, dayType)
```

### DE/FR
```{r}
clusterPlot(data, "DE", "FR", hour, dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
clusterPlot(data, "BE", "NL", hour, dayType)
```


### DE/NL
```{r}
clusterPlot(data, "DE", "NL", hour, dayType)
```

