---
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
params: 
    set_title: ""
title: "`r params$set_title`"
---



```{r setup, include=FALSE}
library(flexdashboard)
library(rAmCharts)
library(manipulateWidget)
library(flowBasedClustering)
library(ggplot2)
library(pipeR)
library(DT)
library(shiny)
library(gridExtra)
```


Cluster {data-navmenu="Hour"}
=====================================


<h1> Typical day, hour : `r data[idDayType == dayType]$TypicalDay` </h1>


Column {data-width=100}
-----------------------------------------------------------------------

### Day in cluster 

```{r}
day <- data[idDayType == dayType]$TypicalDay

datatable(data.frame(Date = as.character(unique(data[idDayType == dayType]$dayIn[[1]][[1]]$Date))), rownames=FALSE, 
          # filter = 'top'
          extensions = 'Buttons',
          options = list(searching=F,
                         paging = F,
                         bInfo = F,
                         pageLength = 10000,
                         dom = 'Bfrtip',
                         buttons = list(
                           list(extend = 'csv',
                                buttons = c('csv'),
                                text = 'Download data',
                                filename = "cluster_typicalDay")
                         )
          )
)



```

Column {.tabset}
-----------------------------------------------------------------------
Hour 1 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 1
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 1
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 1

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 2 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 2
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 2
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 2

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 3 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 3
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 3
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 3

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 4 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 4
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 4
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 4

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 5 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 5
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 5
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 5

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 6 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 6
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 6
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 6

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 7 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 7
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 7
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 7

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 8 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 8
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 8
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 8

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 9 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 9
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 9
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 9

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 10 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 10
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 10
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 10

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 11 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 11
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 11
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 11

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 12 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 12
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 12
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 12

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 13 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 13
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 13
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 13

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 14 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 14
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 14
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 14

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 15 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 15
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 15
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 15

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 16 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 16
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 16
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 16

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 17 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 17
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 17
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 17

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 18 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 18
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 18
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 18

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 19 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 19
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 19
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 19

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 20 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 20
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 20
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 20

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 21 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 21
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 21
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 21

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 22 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 22
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 22
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 22

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 23 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 23
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 23
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 23

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

Hour 24 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 24
```


Column {.tabset}
-----------------------------------------------------------------------
### Historical domains, hour 24
```{r, fig.width=8.5, fig.height=8}

grid.arrange(
  clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE),
  clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE), 
  nrow=2, ncol=2
)
```

### Typical day, hour 24

```{r,  fig.width=10, fig.height=9}
tags$div(
  tags$div(style = "height: 830px; width : 840px",
           combineWidgets(ncol = 2, 
                          clusterPlot(data, "BE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE, 
                                      width = "640px", height = "610px"),
                          clusterPlot(data, "BE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "FR", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE),
                          clusterPlot(data, "DE", "NL", hour, dayType, 
                                      ggplot = FALSE, typicalDayOnly = TRUE)
           )
  ), 
  align = "center")
```

