---
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    css: styles_flex.css
params: 
    set_title: ""
title: "`r params$set_title`"
---



```{r setup, include=FALSE}
library(flexdashboard)
library(rAmCharts)
library(antaresFlowbased)
library(manipulateWidget)
library(flowBasedClustering)
library(ggplot2)
library(pipeR)
library(DT)
library(pipeR)
```


Cluster {data-navmenu="Hour"}
=====================================


<h1> Typical day : `r data[idDayType == dayType]$TypicalDay` </h1>


Column {data-width=100}
-----------------------------------------------------------------------

### Day in cluster 

```{r}
day <- data[idDayType == dayType]$TypicalDay

datatable(data.frame(Date = as.character(unique(data[idDayType == dayType]$dayIn[[1]][[1]]$Date))), rownames=FALSE, 
            # filter = 'top'
        extensions = 'Buttons',
        options = list(searching=F,
                       paging = F,
                       bInfo = F,
                       pageLength = 10000,
                       dom = 'Bfrtip',
                       buttons = list(
                                      list(extend = 'csv',
                                           buttons = c('csv'),
                                           text = 'Download data',
                                           filename = "cluster")
                       )
        )
  )



```


Column {.tabset data-width=1200}
-----------------------------------------------------------------------
Hour 1 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 1
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Historical domains 1
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 1

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Historical domains 1
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 1
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 2 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 2
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 2
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 2
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 2
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 2
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 3 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 3
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 3
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 3
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 3
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 3
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 4 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 4
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 4
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 4
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 4
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 4
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```



Hour 5 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 5
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 5
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 5
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 5
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 5
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```



Hour 6 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 6
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 6
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 6
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 6
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 6
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 7 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 7
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 7
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 7
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 7
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 7
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 8 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 8
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 8
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 8
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 8
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 8
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```



Hour 9 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 9
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 9
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 9
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 9
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 9
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 10 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 10
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 10
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 10
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 10
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 10
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 11 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 11
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 11
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 11
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 11
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 11
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 12 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 12
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 12
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 12
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 12
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 12
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 13 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 13
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 13
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 13
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 13
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 13
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 14 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 14
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 14
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 14
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 14
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 14
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 15 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 15
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 15
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 15
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 15
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 15
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 16 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 16
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 16
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 16
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 16
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 16
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```



Hour 17 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 17
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 17
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 17
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 17
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 17
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 18 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 18
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 18
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 18
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 18
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 18
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 19 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 19
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 19
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 19
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 19
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 19
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 20 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 20
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 20
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 20
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 20
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 20
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 21 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 21
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 21
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 21
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 21
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 21
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```



Hour 22 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 22
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 22
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 22
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 22
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 22
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 23 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 23
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 23
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 23
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 23
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 23
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 24 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 24
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Historical domains 24
```{r}
clusterPlot(data, "BE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 24
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Column {.tabset data-width=500}
------------------------------------------------------------------
### Historical domains 24
```{r}
clusterPlot(data, "DE", "FR", hour, dayType, ggplot = TRUE)
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = TRUE)
```

### Typical day 24
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```
