---
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    css: styles_flex.css
params: 
    set_title: ""
title: "`r params$set_title`"
---



```{r setup, include=FALSE}
library(flexdashboard)
library(rAmCharts)
library(antaresFlowbased)
library(manipulateWidget)
library(flowBasedClustering)
library(ggplot2)
library(pipeR)
```

Hour 1 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 1
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 2 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 2
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 3 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 3
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 4 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 4
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 5 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 5
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 6 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 6
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 7 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 7
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 8 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 8
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 9 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 9
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 10 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 10
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 11 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 11
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 12 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 12
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 13 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 13
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 14 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 14
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 15 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 15
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 16 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 16
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 17 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 17
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Hour 18 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 18
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 19 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 19
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 20 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 20
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 21 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 21
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```
Hour 22 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 22
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 23 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 23
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```

Hour 24 {data-navmenu="Hour"}
=====================================

```{r, echo = FALSE, eval = TRUE}
hour <- 24
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------
### Mean typical day

```{r, fig.height=8}
combineWidgets(clusterPlot(data, "BE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "BE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


Column {.tabset data-width=400}
------------------------------------------------------------------
### Mean typical day
```{r, fig.height=8}
combineWidgets(clusterPlot(data, "DE", "FR", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot(),
clusterPlot(data, "DE", "NL", hour, dayType, ggplot = FALSE, typicalDayOnly = TRUE)%>>%plot())
```


